A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-17 MSR-Scratch.tex
Removed keywords
Updated abstract

\begin{abstract}
Scratch is increasingly popular, both as an introductory programming language and as a research target in the computing education research field.	
In this paper, we present an open dataset of 250K recent Scratch programs from 100K authors scraped from the Scratch project repository.
We processed the program data to encode it into a database that facilitates querying and further analysis. We further enriched the dataset with project metadata and with programming mastery scoring results.
The dataset is intended as an input for research on computing education and source code analysis.
Specifically, it can support assessing the programming skills developed in Scratch, exploring the learning progressions of novice programmers, evaluating the quality of Scratch programs, and identifying smells and bad programming practices.
\end{abstract}

\begin{IEEEkeywords}
Scratch; dataset;
\end{IEEEkeywords}

>>>>

\begin{abstract}
Scratch is increasingly popular, both as an introductory programming language and as a research target in the computing education research field.	
In this paper, we present a dataset of 250K recent Scratch projects from 100K different authors scraped from the Scratch project repository.
We processed the projects' source code and metadata to encode them into a database that facilitates querying and further analysis. We further evaluated the projects in terms of programming skills and mastery, and we included the project scoring results.
The dataset enables the analysis of the source code of Scratch projects, of their quality characteristics, and of the programming skills that their authors exhibit.
The dataset can be used for empirical research in software engineering and computing education.
\end{abstract}
